An Empirical Measurement-Based Analysis for Linux-based Real-Time Multiprocessor Scheduling

### 2017-05-14 paper.tex
Add benchmarking and profiling process and parameter

    A new tool to visualize scheduling is developed, enabling developers to record the scheduler states
    including executing process ID (PID), PID in scheduler run-queue, context switch points, timer interrupt execution,
    scheduling events, etc. on per processor core basis. It differs from profiling based methodology tools, e.g.
    perf \cite{perf}, by means of high fidelity and full-profiling fashion of the target system. It gathers entire
    activities inside Linux kernel in microsecond scale, being able to capture the impact of occasional short-burst
    scheduler events, which only last less that 10us. These events are mostly not shown in the result of sampling based
    measurement which focus on average-case execution time. By analyzing full-detailed record, we can not only
    capture the worst-case execution time (WCET), but also understand the cause of these incidents.

@@

    In addition, mctest would do a series of identically executions and record the execution time of each turn. These records
    can be used to determined the execution jitter of the application on the real-time system, which besides wakeup latency.
    This could be used to reflect to the system-call overhead of the system. We have been utilizing mctest as the testing
    work-load and jitter measurement tool during methodology.

    \begin{figure} \centering \includegraphics[width=3.5in]{img/latency_timeline.png} \caption{Task Wake-up Latency}
    \label{fig:latency_timeline} \end{figure}

@@

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-cpu.png} \caption{Scheduler duration of cyclictest
    with CPU bounded load} \label{fig:sd_cpu} \end{figure}

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-memory.png} \caption{Scheduler duration of cyclictest
    with memory bounded load} \label{fig:sd_memory} \end{figure}

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-io.png} \caption{Scheduler duration distribution of
    cyclictest with I/O bounded load} \label{fig:sd_io} \end{figure}

@@

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-iso.png} \caption{Scheduler duration of cyclictest with
    memory bounded load on different cores} \label{fig:sd_iso} \end{figure}

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-same-no-cache.png} \caption{Scheduler duration of
    cyclictest with memory bounded load on same core} \label{fig:sd_same_no_cache} \end{figure}

>>>>

    A new tool to visualize scheduling is developed, enabling developers to record the scheduler states including
    executing process ID (PID), PID in scheduler run-queue, context switch points, timer interrupt execution, scheduling
    events, etc. on per processor core basis. It differs from profiling based methodology tools, e.g. perf \cite{perf},
    by means of high fidelity and full-profiling fashion of the target system. It gathers entire activities inside Linux
    kernel in microsecond scale, being able to capture the impact of occasional short-burst scheduler events, which only
    last less that 10us. These events are mostly not shown in the result of sampling based measurement which focus on
    average-case execution time. By analyzing full-detailed record, we can not only capture the worst-case execution
    time (WCET), but also understand the cause of these incidents. This scheduler benchmarking process is composed of
    starting a benchmark, cyclictest, and profiler in the same time. Cyclictest were set with "-mnq
    -p 90 --policy=fifo -h 1000 -i 1000 -l 10000." The profiling last 3 seconds. Logs are extracted from the profiler
    and analyzed afterward.

@@

    \begin{figure} \centering \includegraphics[width=3.3in]{img/latency_timeline.png} \caption{Task Wake-up Latency}
    \label{fig:latency_timeline} \end{figure}

@@

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-cpu.png} \caption{Scheduler duration of cyclictest
    with CPU bounded load (stress with 8 cpu threads)} \label{fig:sd_cpu} \end{figure}

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-memory.png} \caption{Scheduler duration of cyclictest
    with memory bounded load (stress with 8 vm threads, vm work size=16M)} \label{fig:sd_memory} \end{figure}

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-io.png} \caption{Scheduler duration distribution of
    cyclictest with I/O bounded load (stress with 8 io threads)} \label{fig:sd_io} \end{figure}

@@

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-iso.png} \caption{Scheduler duration of cyclictest with
    memory bounded load (stress with 8 vm threads, vm work size=16M) on different cores} \label{fig:sd_iso} \end{figure}

    \begin{figure} \centering \includegraphics[width=3in]{img/sd-same-no-cache.png} \caption{Scheduler duration of
    cyclictest with memory bounded load (stress with 8 vm threads, vm work size=16M) on same core} \label{fig:sd_same_no_cache} \end{figure}
